Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students

### 2024-02-15 paper/paper.qmd
Add info about measurement to data section
Add info about measurement to data, amended smartnoise citation

This dataset is obtained from the National Center of Education Statistics [@citeraw2]. For each district, it provides information as to the county and state to which they belong, and their NCES district ID.

@@

This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" GitHub Repository [@kahan2020usbroadband]. According to Kahan [-@kahan2020usbroadband], data consists of broadband usage percentages at the US county-level in October 2020, obtained from anonymised data Microsoft collects. In less technical terms, this means that every time a device receives an update from or connects to a Microsoft service, Microsoft servers make an estimate of its throughput speed and determine its location at the zip-code level. In using the Federal Communications Commission definition of broadband, being 25 megabits per second per download [@FCC], a count is then made of the number of devices that connect to the Internet at broadband speed per zip code. After making such measurements, noise is added to data aggregations using the open-source SmartNoise platform, thereby preventing leakage about specific individuals in the dataset and ensuring differential privacy.

>>>>

This dataset is obtained from the National Center of Education Statistics [@citeraw2]. For each district, it provides information as to the county and state to which they belong, and their NCES district ID. Note that unique NCES ID numbers are automatically assigned to districts upon being reported to the US Department of Education by their state education agency via the platform EDFacts [@citeraw2].

@@

This dataset is available from Microsoft’s “United States Broadband Usage Percentages Dataset" GitHub Repository [@kahan2020usbroadband]. According to Kahan [-@kahan2020usbroadband], data consists of broadband usage percentages at the US county-level in October 2020, obtained from anonymised data Microsoft collects. In less technical terms, this means that every time a device receives an update from or connects to a Microsoft service, Microsoft servers make an estimate of its throughput speed and determine its location at the zip-code level. In using the Federal Communications Commission definition of broadband, being 25 megabits per second per download [@FCC], a count is then made of the number of devices that connect to the Internet at broadband speed per zip code. After making such measurements, noise is added to data aggregations using the open-source SmartNoise platform, thereby preventing leakage about specific individuals in the dataset and ensuring differential privacy [@SmartNoise_2023].
